### 2025-07-24 paper/experiments/README.qmd
done

The Julia scripts introduced above look for certain environment variables pertaining to the configurations of experiments and evaluations, as well as paths to directories that will used to store results. Before running batch jobs, you therefore want to specify these variables as illustrated in the following example:

```
export CONFIG=paper/experiments/configs/single.toml   # path to configuration file
export OUTPUT_SUBDIR="final_run"                      # path to store outputs (root directory is /paper/experiments/output by default)
```

@@

@@

The chart in Figure 1 of the paper is produced in [paper/sections/other/constraints.qmd](paper/sections/other/constraints.qmd).

@@

The chart in Figure 2 of the paper can be reproduced using the following script: [paper/experiments/mnist_chart.jls](/paper/experiments/mnist_chart.jls).

@@

The chart in Figure 3 of the paper is produced in [paper/sections/other/main_results.qmd](paper/sections/other/main_results.qmd).

>>>>

The Julia scripts introduced above look for certain environment variables pertaining to the configurations of experiments and evaluations, as well as paths to directories that will used to store results. Some of the environment variables specified in a `.env` file. Before running batch jobs, you therefore want to specify these variables as illustrated in the following example:

```
source .env                                           # declares a few environment variables
export CONFIG=paper/experiments/configs/single.toml   # path to configuration file
export OUTPUT_SUBDIR="final_run"                      # path to store outputs (root directory is /paper/experiments/output by default)
```

@@

### Cluster Jobs

To run jobs on a cluster, you can use any of bash scripts under `paper/experiments/jobs/`. Assuming you have already exported environment variables as discussed above, you can run cluster jobs as follows:

```
sbatch --time=00:30:00 --ntasks=20 --cpus-per-task=$NTHREADS $RUN_GRID_SEQ --model=mlp --tau=0.5 --reg_strength=0.01 --data=lin_sep
```

Here we have specified a run time, `--time`, the number of processes to be used, `--ntasks`, and how many threads to use (defaults to 1). The `$RUN_GRID_SEQ` variable points to `paper/experiments/jobs/run_grid_sequentially.sh`. The remaining variables are supplied as `ARGS` to Julia and can be used to configure the experiment, as already discussed above.

@@

The chart in Figure 1 of the paper is produced in [paper/sections/other/constraints.qmd](../sections/other/constraints.qmd).

@@

The chart in Figure 2 of the paper can be reproduced using the following script: [paper/experiments/mnist_chart.jls](mnist_chart.jls).

@@

The chart in Figure 3 of the paper is produced in [paper/sections/other/main_results.qmd](../sections/other/main_results.qmd). Integrated gradients were computed using [paper/experiments/integrated_gradients_mnist.jl](integrated_gradients_mnist.jl)

### Integrated Gradients

The results for integrated gradients presented in the appendix can be reproduced using [paper/experiments/run_integrated_gradients.jl](run_integrated_gradients.jl).

### 2025-07-24 paper/preprint/appendix.tex
done

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-train-default}: Training Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-eval-default}: Evaluation Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

Let \(\mathbb{g}_d\) denote the estimated IG for feature \(d\). Then in
the case of 2D synthetic datasets we find that taking the absolute value
of the outputs, \(|\mathbb{g}_d|\), and then dividing them by a
\(\max(\mathbb{g}) - \min(\mathbb{g})\) term allows us to make the most
meaningful comparison. In the case of real-world datasets we choose to
normalize the values to a 0-1 range instead.

@@

\caption{\label{tbl-ig}Integrated gradients.}

@@

\caption{\label{fig-mnist-ig}Class-conditional integrated gradients.}

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-train-final-run-train}: Training Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-tune-train}: Training Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-tune_lr-train}: Training Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

@@

\begin{tcolorbox}[enhanced jigsaw, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, leftrule=.75mm, coltitle=black, colback=white, toprule=.15mm, opacityback=0, colbacktitle=quarto-callout-note-color!10!white, breakable, toptitle=1mm, bottomrule=.15mm, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, rightrule=.15mm, arc=.35mm, titlerule=0mm, left=2mm, opacitybacktitle=0.6]

>>>>

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-default}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-eval-default}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

Let \(\mathbf{g}_d\) denote the estimated IG for feature \(d\). Then in
the case of 2D synthetic datasets we find that taking the absolute value
of the outputs, \(|\mathbf{g}_d|\), and then dividing them by a
\(\max(\mathbf{g}) - \min(\mathbf{g})\) term allows us to make the most
meaningful comparison. In the case of real-world datasets we choose to
normalize the values to a 0-1 range instead.

@@

\caption{\label{tbl-ig}Average sensitivity \(\pm\) bootstrapped standard
errors of protected features as per standardized integrated gradients.}

@@

\caption{\label{fig-mnist-ig}Class-conditional standardized integrated
gradients for MNIST. Top: BL. Bottom: CT. Mutability constraints were
imposed on the five top and bottom rows of pixels.}

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-final-run-train}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune-train}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune_lr-train}: Training Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, colframe=quarto-callout-note-color-frame, bottomtitle=1mm, titlerule=0mm, arc=.35mm, breakable, toprule=.15mm, left=2mm, colbacktitle=quarto-callout-note-color!10!white, coltitle=black, colback=white, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, opacityback=0]

### 2025-07-24 paper/sections/other/main_results.qmd
done

Let $\mathbb{g}_d$ denote the estimated IG for feature $d$. Then in the case of 2D synthetic datasets we find that taking the absolute value of the outputs, $|\mathbb{g}_d|$, and then dividing them by a $\max(\mathbb{g}) - \min(\mathbb{g})$ term allows us to make the most meaningful comparison. In the case of real-world datasets we choose to normalize the values to a 0-1 range instead.

We compare the (average) sensitivity to the features that were protected for CT models. We again use bootstrapping (100 rounds, 2500 samples per round) to establish the significance of our results. These are presented in @tbl-ig.

@@

Integrated gradients.

@@

![Class-conditional integrated gradients.](/paper/figures/mnist_ig.png){#fig-mnist-ig}

>>>>

Let $\mathbf{g}_d$ denote the estimated IG for feature $d$. Then in the case of 2D synthetic datasets we find that taking the absolute value of the outputs, $|\mathbf{g}_d|$, and then dividing them by a $\max(\mathbf{g}) - \min(\mathbf{g})$ term allows us to make the most meaningful comparison. In the case of real-world datasets we choose to normalize the values to a $[0,1]$ range instead. We compare the (average) sensitivity to the features that were protected for CT models. Once again we use bootstrapping (100 rounds, 2500 samples per round) to establish the significance of our results. These are presented in @tbl-ig.

@@

Average sensitivity $\pm$ bootstrapped standard errors of protected features as per standardized integrated gradients.

@@

![Class-conditional standardized integrated gradients for MNIST. Top: BL. Bottom: CT. Mutability constraints were imposed on the five top and bottom rows of pixels.](/paper/figures/mnist_ig.png){#fig-mnist-ig}
